### 2016-05-29 Paper/paper.tex
more or less done

\section{Introduction}
\citet{Sykulski2016} present a multi-component spectral model for analysis of data transmitted by ocean surface drifters. 
Drifters are free-floating  instruments that transmit their location at regular time intervals,  creating a \textbf{\it{Langrangian time series}}, or a sequence of spatial locations over time. 
Figure \ref{fig: fig1} shows a sample 250-day drifter trajectory. 
Oceanographers use these time series to increase understanding of  ocean circulation patterns.
Published in January 2016 in the \textbf{\it{Journal of the Royal Statistical Society Series C}}, this paper makes a notable contribution to the statistical literature by illustrating how to directly embed knowledge of a physical system into a stochastic model. 
 \begin{figure}[h!]
  \centering
    \includegraphics[width=.6\textwidth]{ReplicatedFigures/fig1.pdf}
        \caption{A 250-day sample drifter trajectory with two 50-day periods highlighted in green and blue. The time period highlighted in green is not affected by an eddy while the time period highlighted  in blue is.}
        	\label{fig: fig1}
\end{figure}

@@

	\subsection{Spectral Analysis}
	\label{sec: specAnalysis}
	\indent We briefly review spectral analysis as all the analysis in \citet{Sykulski2016} is done in the spectral domain.   
	More thorough coverage of this material can be found in  \citep{Percival1993}, for example. 
	From a statistical perspective, a time series, $z(t)$, real or complex-valued,  can be understood as a realization of a stochastic process over time, where  $t = \{1,2,...,n\}$ index the observed time points.  
	Time series are often modeled as the sums of periodic functions, which, using Euler's formula, can be represented compactly as sums of appropriately-weighted complex exponentials. 
	Moreover, data in the time domain can easily be related to data in the frequency domain and vice versa using the Fourier or inverse Fourier transformations:
	\hdcomment{these are wrong} 	
	\begin{align}
z(t) = \int_{-\infty}^{\infty} f_{z}(\omega)e^{i\omega t}d\omega,&& f_{z}(\omega) = \int_{-\infty}^{\infty} z(t) e^{-i \omega t }dt.
\end{align}
\citep{Percival1993}. 
To understand the distribution of frequencies, the \textbf{\it{power spectral density}},
\begin{equation}
S(\omega) = \underset{T \rightarrow \infty}{\lim} \mathbb{E} \left(\frac{1}{2T} \left| \int_{-T}^{T} z(t) e^{-i \omega t}dt \right|^{2} \right),
\end{equation}
is often employed. 
This quantity represents the variance (or power) associated with each frequency \citep{Percival1993}. 
Power spectral densities are useful for statistical modeling and can be related to the autocovariance sequence of a time series using  Fourier transformation.  
We define the autocovariance  for $z(t)$ as $s(\tau) = \mathbb{E}[z(t) z^{*}(t - \tau)] $ where $z^{*}(t)$ represents the complex conjugate of z(t). Letting $\tau$ be the time lag, we have
\begin{align}
\label{eq: fourierPair}
S(\omega) = \int_{-\infty}^{\infty}s(\tau) e^{-i\omega t}d \tau \Longleftrightarrow s(\tau) = \frac{1}{2\pi} \int_{-\infty}^{\infty}S(\omega) e^{i \omega t} d\omega 
\end{align}

\noindent \citep{Sykulski2013}. For an observed time series, the power spectral density is often estimated with the periodogram, where 
\begin{equation}
\label{eq: perio}
\hat{S}(\omega) = \frac{\Delta}{N} \left( \sum_{t=1}^{N} z(t) e^{-i \omega t} \right)^{2}
\end{equation}
\citep{Sykulski2013}. 
Although intuitively appealing, this estimator has known problems that stem from  sampling a time series at discrete intervals. 
\textbf{\it{Aliasing}} refers to the fact that frequencies above the highest observable frequency cannot be captured, and, are instead, confounded with other frequencies in the spectrum.  
\hdcomment{Get this right!} Additionally, \textbf{\it{Leakage}} refers to the effects of because Fourier transforms are applied are a smooth, create discontinuities
$\textbf{\it{Tapering}}$ reduces leaking by \hdcomment{get this right!}
However, depending on how tapering is used, it can introduce its own  biases in estimation.

@@

\subsubsection{Inertial oscillations}
We begin by discussing the model for the inertial oscillations. 
In a deterministic setting, inertial oscillations are often modeled with the following set of coupled differential equations
\begin{align}
\label{eq: deterOsc}
\frac{\partial u }{\partial t}  + f_{0} \nu &= F - cu,\\ \nonumber
\frac{\partial v}{\partial t} - f_{0}u &= G - cv,
\end{align}
where $u$ and $v$ again represent eastward and northward velocities, $f_{0}$ represents the inertial frequency in radians per unit time, and $F$ and $G$ are forces related to the wind  \citep{Pollard1970}. 
Suppressing the dependence on $t$ and using the complex representation of the velocity,  we show that these relationships can be equivalently expressed as follows
\begin{align}
\label{eq:diffEqDeriv}
\nonumber
\frac{dz}{dt} &= \frac{\partial u}{dt} + i\frac{\partial v(t)}{dt} \\ \nonumber
dz &= (F - c u- f_{0}v)dt + i(G - cv + f_{0}u)dt\\ \nonumber
&= f_{0}(-v + iu)dt - c(u + iv)dt + (F + iG)dt\\ \nonumber
&= if_{0}(u + iv)dt - c(u + iv)dt + (F + iG)dt\\ 
&= (if_{0} - c)z dt + (F + iG)dt. 
\end{align}
\citet{Sykulski2016} further replace the wind forcing term, $(F + iG)dt$  with complex-valued Brownian increments \citep{Mandelbrot1968} to obtain a stochastic analogue for Equation \ref{eq:diffEqDeriv},
 \begin{equation}
\label{eq: ouEq}
dz(t) = (i f_{0} -c) z(t) dt + A d Q(t). 
\end{equation}  
Equation \ref{eq: ouEq}  is known as the complex-valued Ornstein-Uhlenbeck (OU) stochastic differential equation. 
In general,  OU processes are considered continuous-time equivalents to the AR(1) process. Specifically,  the univariate OU process is the only mean-zero, stationary, Gaussian, and continuous Markov process, and, similarly the multivariate OU process is the only mean-zero $K$-variate process that is stationary, continuous, Gaussian, and Markov \citep{Schach1971}.
 The complex-valued OU process is the complex representation of a bivariate OU process.  
 In the formulation of Equation \ref{eq: ouEq}, $c > 0$ is a dampening parameter that forces the process to always eventually return to its mean position, $z = 0$.  
 The final term of Equation \ref{eq: ouEq} is a positive constant, $A$, multiplied by $dQ(t)$.  The term $Q(t), t \geq 0$ is a standard complex Wiener process,  meaning $Q(t) = Q_{1}(t) + i Q_{2}(t)$, where $Q_{1}(t)$ and $Q_{2}(t)$ are standard Wiener processes.
 We remind the reader that Wiener processes are the stochastic models originally used to represent Brownian motion. 
  Such a process $\{Q(t, \omega): t \geq 0\}$ on the measure space $(\omega, Q, P)$ must satisfy
\begin{enumerate}
\item $Q(0, \omega) = 0$ almost everywhere
\item $\{Q(t, \omega): t \geq 0\}$ is distributed normally on $(\Omega,Q, P)$
\item $Q(t + \tau, \omega) - Q(t, \omega)$ has mean 0 and variance $\tau$ for all $t, \tau > 0$
\end{enumerate}
\citep{Hida1980}.

To identify and estimate shifts in the angular frequency, presumably caused by eddies, \citet{Sykulski2016} propose replacing the known inertial requency, $f_{0}$,  in Equation \ref{eq: ouEq} with  a free parameter, $\omega_{0}$, to be estimated by the data. 
If the estimated angular frequency differs from the inertial frequency, the angular frequency of the eddy can be calculated as $\omega_{eddy} = f_{0} - \omega_{0}$, since $\omega_{0}$ is a sum of the inertial and eddy frequencies.

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=.7\textwidth]{ReplicatedFigures/fig3.pdf}
        \caption{Simulated velocities obtained using FBM (blue) and Mat\'{e}rn (red)  processes. Top Left: The eastward component of the velocities. Top Right: The eastward and northward components of the velocities. Bottom: Periodograms of both processes on the decibel scale. \vmcomment{I would include legends or direct labeling for all your figures.}}
        	\label{fig: fmbMat}
\end{figure}

\subsubsection{Overall Model}
Combining the inertial oscillation and turbulent background parts of the model is straightforward.
 To find both the autocovariance and power spectral densities, we can simply add the corresponding components of the inertial oscillation and turbulent background autocovariances. 
 Using Equations \ref{eq: ouAC} and \ref{eq:maternAC} and Equations \ref{eq:ouPSD} and\ref{eq:maternPSD}, we obtain
\begin{align}
\label{eq: fullSpec}
s(\tau ;\boldsymbol{\theta}) &= \frac{A^{2}}{2c} \exp(i \omega_{0}\tau) \exp(-c|\tau|) +  \frac{B^{2}}{2^{\alpha - 1/2}\pi^{1/2} \Gamma(\alpha) h^{2 \alpha - 1}}(h|\tau|)^{\alpha - 1}\mathcal{K}_{\alpha - 1/2}(h|\tau|)
,\\
S(\omega; \boldsymbol{\theta}) &= \frac{A^{2}}{(\omega - \omega_{0}) + c^{2}} + \frac{B^{2}}{(\omega^{2} + h^{2})^{\alpha}}.
\end{align}

\subsection{Fitting the Model}
\subsubsection{Blurred Whittle likelihood}
\par A recent technique introduced by \citet{Sykulski2013}  is used to fit the model.
 Referred to as \textbf{\it{blurred Whittle likelihood}}, this new likelihood builds on the well-known Whittle likelihood, a frequency-based approximation  to the time-domain likelihood that reduces computational cost. 
  Whittle likelihood is designed to approximate the likelihood for a univariate Gaussian process, $\boldsymbol{Z}$,  in the time domain that has the likelihood
\begin{align*}
l_{t}(\boldsymbol{\theta}) = - \frac{1}{2} \log \left|\boldsymbol{\Sigma}_{Z}(\boldsymbol{\theta}) \right| - \frac{1}{2} Z^{T} \boldsymbol{\Sigma}_{\boldsymbol{Z}}^{-1}(\boldsymbol{\theta})\boldsymbol{Z},
\end{align*}
where $\boldsymbol{\theta}$ are the model parameters for a particular choice of covariance structure, $\boldsymbol{\Sigma}_{z}$,  and $t$ denotes the time domain  \citep{Sykulski2013}.

 It is known that  the periodogram satisfies
\begin{equation}
\hat{S}(\omega) \overset{d}{\rightarrow} S(\omega) \chi^{2}_{2}/2
\end{equation}
under certain regularity conditions \citep{Contreras2006}. 
\citet{Whittle1953} combined this result with Fourier approximations to the true covariance structure and features of Toeplitz matrices to obtain the approximate likelihood
\begin{align}
\label{eq: bwl}
l_{\omega}(\boldsymbol{\theta}) 
&= -\sum_{\omega \in \Omega} \left[ \frac{\hat{S}(\omega)}{S(\omega;\boldsymbol{\theta})}  + \log  \{ S(\omega; \boldsymbol{\theta}) \}\right],
\end{align}
where the subscript $w$ indicates that this is a Whittle likelihood. 
Leveraging the fast Fourier transform \citep{Cooley1965}, this  likelihood can be evaluated in $\mathcal{O}(N log(N))$, where $N$ is the length of the time series. 
This is a notable increase in speed compared to the $\mathcal{O}(N^{3})$  required for time-domain likelihood  \citep{Sykulski2016}. 
  Nevertheless, this likelihood relies on the periodogram and so is affected by aliasing and leakage as discussed in Section \ref{sec: specAnalysis}.

To improve on these problems, \citet{Sykulski2013} propose replacing the theoretical spectrum, $S(\omega; \theta)$\, in Equation \ref{eq: bwl} with the expected value of the periodogram, 
\begin{equation}
\overline{S}(\omega; \boldsymbol{\theta}) = \Delta \sum_{\tau = - (N - 1)}^{N-1} \left(1 - \frac{|\tau|}{N} \right)s(\tau ; \boldsymbol{\theta}) \exp ( - i \omega \tau \Delta).
\end{equation} 
This form of the expected periodogram can be shown to be equivalent to convolving the theoretical spectrum with the Fej\'{e}r kernel 
\begin{equation}
\mathcal{F}(\cdot) = \frac{\Delta}{2\pi N} \frac{\sin^{2}(N \omega \Delta/2)}{\sin^{2}(\omega \Delta /2)} 
\end{equation} \citep{Sykulski2013}. 
This improves the estimators obtained through maximizing the likelihood, because the expected value of the periodogram $\mathbb{E}[|J_{Z}(\omega)^{2}]$ is blurred in the same way as the observed periodogram \hdcomment{sentence wrong, look this up!}. Also, aliasing effects due to sampling at discrete intervals are taken into account. 
This leads to the final likelihood
\begin{align}
l_{b}(\boldsymbol{\theta}) = - \sum_{\omega \in \Omega} \left[\frac{\hat{S}(\omega)}{\overline{S}(\omega; \boldsymbol{\theta})} + \log \{ \overline{S} (\omega; \boldsymbol{\theta}) \}\right],
\end{align}
where $b$ denotes blurred. This likelihood is maximized by standard off-the-shelf nonlinear optimization techniques. (Specifically, \citet{Sykulski2016} uses the `fminsearchbnd' function in Matlab \citep{DErrico2006} and we use the `fminsearch' function in the `pracma' R package \citep{Borchers2015}.)

@@

\subsubsection{Significance tests for simpler models}
\label{sec: sig}
Finally, \citet{Sykulski2016} propose that a simple likelihood ratio test can be used at each time period to test whether or not a shift in the inertial oscillation has occurred. 
To do so, the authors suggest fitting a simpler five parameter model where the the parameter $\omega_{0}$ is fixed to be the inertial frequency $f_{0}$. 
Then this simpler model can be compared to the full six parameter model via a likelihood ratio test with test statistic
\begin{equation}
\label{eq: LRT}
R(t) = 2[l_{b} \{\hat{\theta}_{1}(t) \} - l_{b}\{\hat{\theta}_{0}(t) \} ],
\end{equation}
where $\hat{\theta}_{0}(t)$ is the fitted parameter vector for the simpler, or null model, and $\hat{\theta}_{1}(t)$ is the fitted parameter vector for the full model.
 The authors claim $R(t)$ then follows a chi-squared distribution with 1 degree of freedom. 
 However, as we will discuss further this may be overly simplistic, because of potential identifiability issues with the parameters and lack of independence between time points stemming from the use of a rolling window.

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=.8\textwidth]{ReplicatedFigures/fig5.png}
        \caption{Left: The spectral density of one particle (blue) with the model fit overlaid for the portion of the spectra used to fit it (green) and extended to all frequencies (red). Right: The ensemble mean periodogram (blue) with the ensemble fit for the frequencies used to fit it (green) and extended to the entire spectrum (red). Individual trajectories' periodograms (light grey) and model fits (dark fit) are also displayed. }
        \label{fig: fig5}
\end{figure}

@@

   \begin{figure}[h!]
  \centering
    \includegraphics[width=.9\textwidth]{ReplicatedFigures/fig7.png}
        \caption{Top: Observed spectra of the drifter over time; Bottom: Modeled spectra over time. On both figures, the semi-transparent gray line indicates the average inertial frequency within the rolling window at the current time period.  Only frequencies used in the estimation are included.  }
        	\label{fig:timeVarying}
\end{figure}

 \par
 We also display the fitted parameter values over time and their 95$\%$ confidence interval bands in Figure \ref{fig: fig8}. 
The 95$\%$ intervals are obtained using numerical calculation of the Hessian.
The parameters all change smoothly over time. 
We note that the inertial frequency differs from the Coriolis Frequency from roughly days 600 to 900. 
\citet{Sykulski2016} note that this deviation is appropriate and can be explained by a change in tidal energy over shallow periods of water. 
 \begin{figure}[h!]
  \centering
    \includegraphics[width=.8\textwidth]{ReplicatedFigures/fig8.png}
        \caption{Estimates of the six model parameters overtime with 95$\%$ confidence interval bands. The red line in the top figure is the inertial frequency.}
        	\label{fig: fig8}
\end{figure}

 \begin{figure}[h!]
  \centering
    \includegraphics[width=.85\textwidth]{ReplicatedFigures/fig9.pdf}
        \caption{Time series of the likelihood ratio test statistic comparing the 5-parameter to 6-parameter models. The dotted red line indicates the value at which test statistics indicate a significant difference between the model. }
        	\label{fig: fig9}
\end{figure}

@@

\par We, however, are skeptical of this use of simple hypothesis testing. 
The parameters are being estimated repeatedly using a rolling window. 
This means that there is not independence between the time periods and there is repeated testing. 
Both of these issues should be accounted for in designing a hypothesis test. 
Further, the authors acknowledge elsewhere in the paper that the length of the rolling window is currently selected empirically and that further work on selecting windows would be beneficial. 
This suggests that the p-value for any time point could be easily influenced by the length of the window used in fitting it.
Thus, robustness checks of this method to the length of the window would be appropriate prior to using it.
In other words, further thought should go in to designing a hypothesis that accurately reflects the problem set-up and modeling.

 \begin{figure}[h!]
  \centering
    \includegraphics[width=.6\textwidth]{ReplicatedFigures/fig10.pdf}
        \caption{Table of the average correlation between parameters. Note that the parameters are ordered differently than in the paper, due to differences in the structure of the author's and my code. There are also minor differences in the correlation values, particularly for values close to zero. These differences can be attributed to slight differences in the numerical optimization used by R and Matlab in calculating the Hessian. }
        	\label{fig: fig10}
\end{figure}

>>>>

\section{Introduction}
\citet{Sykulski2016} present a multi-component spectral model for analysis of data transmitted by ocean surface drifters. 
Drifters are free-floating  instruments that transmit their location at regular time intervals,  creating a \textbf{\it{Langrangian time series}}, or a sequence of spatial locations over time. 
Figure \ref{fig: fig1} shows a sample 250-day drifter trajectory. 
Oceanographers use these time series to increase understanding of  ocean circulation patterns.
Published in January 2016 in the \textbf{\it{Journal of the Royal Statistical Society Series C}}, this paper makes a notable contribution to the statistical literature by illustrating how to directly embed knowledge of a physical system into a stochastic model. 
 \begin{figure}[h!]
  \centering
    \includegraphics[width=.6\textwidth]{ReplicatedFigures/fig1.pdf}
        \caption{A 250-day sample drifter trajectory with two 50-day periods highlighted in green and blue. The time period highlighted in green is not affected by eddies while the time period highlighted in blue is.}
        	\label{fig: fig1}
\end{figure}

@@

	\subsection{Spectral Analysis}
	\label{sec: specAnalysis}
	\indent We briefly review spectral analysis as all the analysis in \citet{Sykulski2016} is done in the spectral domain.   
	More thorough coverage of this material can be found in  \citet{Percival1993}, for example. 
	From a statistical perspective, a time series, $z(t)$, real or complex-valued,  can be understood as a realization of a stochastic process over time, where  $t = \{1,2,...,n\}$ index the observed time points.  
	Time series are often modeled as the sums of periodic functions, which, using Euler's formula, can be represented compactly as sums of appropriately-weighted complex exponentials. 
	Moreover, data in the time domain can easily be related to data in the frequency domain and vice versa using the Fourier or inverse Fourier transformations,
	\begin{align}
Z_{m} = \frac{1}{2T} \int_{-T}^{T}z(t)e^{-i\omega_{m}t} dt && z(t) = \sum_{m=-\infty}^{\infty}Z_{m}e^{i \omega_{m} t},
\end{align}
where $T$ indicates the period \citep{Percival1993}. 
To understand the distribution of frequencies, the \textbf{\it{power spectral density}},
\begin{equation}
S_{z}(\omega) = \underset{T \rightarrow \infty}{\lim} \mathbb{E} \left(\frac{1}{2T} \left| \int_{-T}^{T} z(t) e^{-i \omega t}dt \right|^{2} \right),
\end{equation}
is often employed. 
This quantity represents the variance (or power) associated with each frequency \citep{Percival1993}. 
Power spectral densities are useful for statistical modeling and can be related to the autocovariance sequence of a time series using  Fourier transformation.  
We define the autocovariance  for $z(t)$ as $s(\tau) = \mathbb{E}[z(t) z^{*}(t - \tau)] $ where $z^{*}(t)$ represents the complex conjugate of z(t). Letting $\tau$ be the time lag, we have
\begin{align}
\label{eq: fourierPair}
S_{z}(\omega) = \int_{-\infty}^{\infty}s_{z}(\tau) e^{-i\omega t}d \tau \Longleftrightarrow s_{z}(\tau) = \frac{1}{2\pi} \int_{-\infty}^{\infty}S_{z}(\omega) e^{i \omega t} d\omega 
\end{align}

\noindent \citep{Percival1993}. For an observed time series, the power spectral density is often estimated with the periodogram, where 
\begin{equation}
\label{eq: perio}
\hat{S}_{z}(\omega) = \frac{\Delta}{N} \left( \sum_{t=1}^{N} z(t) e^{-i \omega t \Delta} \right)^{2}
\end{equation}
\citep{Sykulski2013}. 
Although intuitively appealing, this estimator has known problems that stem from  sampling a time series at discrete intervals. 
Specifically, \textbf{\it{Aliasing}} refers to the fact that frequencies above the highest observable frequency cannot be captured, and, are instead, confounded with other frequencies in the spectrum.  
\textbf{\it{Leakage}} describes how as a result of convolution, power from one part of the spectral density function can be transferred to another part of the density.

@@

\subsubsection{Inertial oscillations}
We begin by discussing the model for the inertial oscillations. 
In a deterministic setting, inertial oscillations are often modeled with the following set of coupled differential equations
\begin{align}
\label{eq: deterOsc}
\frac{\partial u }{\partial t}  + f_{0} \nu &= F - cu,\\ \nonumber
\frac{\partial v}{\partial t} - f_{0}u &= G - cv,
\end{align}
where $u$ and $v$ again represent eastward and northward velocities, $f_{0}$ represents the inertial frequency in radians per unit time, and $F$ and $G$ are forces related to the wind  \citep{Pollard1970}. 
Suppressing the dependence on $t$ and using the complex representation of the velocity,  we show that these relationships can be equivalently expressed as follows
\begin{align}
\label{eq:diffEqDeriv}
\nonumber
\frac{dz}{dt} &= \frac{\partial u}{dt} + i\frac{\partial v(t)}{dt} \\ \nonumber
dz &= (F - c u- f_{0}v)dt + i(G - cv + f_{0}u)dt\\ \nonumber
&= f_{0}(-v + iu)dt - c(u + iv)dt + (F + iG)dt\\ \nonumber
&= if_{0}(u + iv)dt - c(u + iv)dt + (F + iG)dt\\ 
&= (if_{0} - c)z dt + (F + iG)dt. 
\end{align}
\citet{Sykulski2016} further replace the wind forcing term, $(F + iG)dt$  with complex-valued Brownian increments \citep{Mandelbrot1968} to obtain a stochastic analogue for Equation \ref{eq:diffEqDeriv},
 \begin{equation}
\label{eq: ouEq}
dz(t) = (i f_{0} -c) z(t) dt + A d Q(t). 
\end{equation}  
Equation \ref{eq: ouEq}  is known as the complex-valued Ornstein-Uhlenbeck (OU) stochastic differential equation. 
In general,  OU processes are considered continuous-time equivalents to the AR(1) process. Specifically,  the univariate OU process is the only mean-zero, stationary, Gaussian, continuous Markov process, and, similarly the multivariate OU process is the only mean-zero $K$-variate process that is stationary, continuous, Gaussian, and Markov \citep{Schach1971}.
 The complex-valued OU process is the complex representation of a bivariate OU process.  
 In the formulation of Equation \ref{eq: ouEq}, $c > 0$ is a dampening parameter that forces the process to always eventually return to its mean position, $z = 0$.  
 The final term of Equation \ref{eq: ouEq} is a positive constant, $A$, multiplied by $dQ(t)$.  The term $Q(t), t \geq 0$ is a standard complex Wiener process,  meaning $Q(t) = Q_{1}(t) + i Q_{2}(t)$, where $Q_{1}(t)$ and $Q_{2}(t)$ are standard Wiener processes.
 We remind the reader that Wiener processes are the stochastic models originally used to represent Brownian motion. 
  Such a process $\{Q(t, \omega): t \geq 0\}$ on the measure space $(\omega, Q, P)$ must satisfy
\begin{enumerate}
\item $Q(0, \omega) = 0$ almost everywhere
\item $\{Q(t, \omega): t \geq 0\}$ is distributed normally on $(\Omega,Q, P)$
\item $Q(t + \tau, \omega) - Q(t, \omega)$ has mean 0 and variance $\tau$ for all $t, \tau > 0$
\end{enumerate}
\citep{Hida1980}.

To identify and estimate shifts in the angular frequency, presumably caused by eddies, \citet{Sykulski2016} propose replacing the known inertial requency, $f_{0}$,  in Equation ~\ref{eq: ouEq} with  a free parameter, $\omega_{0}$, to be estimated by the data. 
If the estimated angular frequency differs from the inertial frequency, the angular frequency of the eddy can be calculated as $\omega_{eddy} = f_{0} - \omega_{0}$, since $\omega_{0}$ is a sum of the inertial and eddy frequencies.

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=.9\textwidth]{ReplicatedFigures/fig3.pdf}
        \caption{Simulated velocities obtained using FBM (blue) and Mat\'{e}rn (red)  processes. Top Left: The eastward component of the velocities. Top Right: The eastward and northward components of the velocities. Bottom: Periodograms of both processes on the decibel scale.}
        	\label{fig: fmbMat}
\end{figure}

\subsubsection{Overall Model}
Combining the inertial oscillation and turbulent background parts of the model is straightforward.
 To find both the autocovariance and power spectral densities, we can simply add the corresponding components of the inertial oscillation and turbulent background autocovariances. 
 Using Equations \ref{eq: ouAC} and \ref{eq:maternAC} and Equations \ref{eq:ouPSD} and \ref{eq:maternPSD}, we obtain
\begin{align}
\label{eq: fullSpec}
s(\tau ;\boldsymbol{\theta}) &= \frac{A^{2}}{2c} \exp(i \omega_{0}\tau) \exp(-c|\tau|) +  \frac{B^{2}}{2^{\alpha - 1/2}\pi^{1/2} \Gamma(\alpha) h^{2 \alpha - 1}}(h|\tau|)^{\alpha - 1}\mathcal{K}_{\alpha - 1/2}(h|\tau|)
,\\
S(\omega; \boldsymbol{\theta}) &= \frac{A^{2}}{(\omega - \omega_{0}) + c^{2}} + \frac{B^{2}}{(\omega^{2} + h^{2})^{\alpha}}.
\end{align}

\subsection{Fitting the Model}
\subsubsection{Blurred Whittle likelihood}
\par A recent technique introduced by \citet{Sykulski2013}  is used to fit the model.
 Referred to as \textbf{\it{blurred Whittle likelihood}}, this new likelihood builds on the well-known Whittle likelihood, a frequency-based approximation  to the time-domain likelihood that reduces computational cost. 
  Whittle likelihood is designed to approximate the likelihood for a univariate Gaussian process, $\boldsymbol{Z}$,  in the time domain that has the likelihood
\begin{align*}
l_{t}(\boldsymbol{\theta}) = - \frac{1}{2} \log \left|\boldsymbol{\Sigma}_{z}(\boldsymbol{\theta}) \right| - \frac{1}{2} Z^{T} \boldsymbol{\Sigma}_{z}^{-1}(\boldsymbol{\theta})\boldsymbol{Z},
\end{align*}
where $\boldsymbol{\theta}$ are the model parameters for a particular choice of covariance structure, $\boldsymbol{\Sigma}_{z}$,  and $t$ denotes the time domain  \citep{Sykulski2013}.

 It is known that  the periodogram satisfies
\begin{equation}
\hat{S}_{z}(\omega) \overset{d}{\rightarrow} S(\omega) \chi^{2}_{2}/2
\end{equation}
under certain regularity conditions \citep{Contreras2006}. 
\citet{Whittle1953} combined this result with Fourier approximations to the true covariance structure and features of Toeplitz matrices to obtain the approximate likelihood
\begin{align}
\label{eq: bwl}
l_{\omega}(\boldsymbol{\theta}) 
&= -\sum_{\omega \in \Omega} \left[ \frac{\hat{S}_{z}(\omega)}{S(\omega;\boldsymbol{\theta})}  + \log  \{ S(\omega; \boldsymbol{\theta}) \}\right],
\end{align}
where the subscript $w$ indicates that this is a Whittle likelihood. 
Leveraging the fast Fourier transform \citep{Cooley1965}, this  likelihood can be evaluated in $\mathcal{O}(N log(N))$, where $N$ is the length of the time series. 
This is a notable increase in speed compared to the $\mathcal{O}(N^{3})$  required for time-domain likelihood  \citep{Sykulski2016}. 
  Nevertheless, this likelihood relies on the periodogram and so is affected by aliasing and leakage as discussed in Section \ref{sec: specAnalysis}.

To improve on these problems, \citet{Sykulski2013} propose replacing the theoretical spectrum, $S(\omega; \boldsymbol{\theta})$\, in Equation \ref{eq: bwl} with the expected value of the periodogram, 
\begin{equation}
\overline{S}(\omega; \boldsymbol{\theta}) = \Delta \sum_{\tau = - (N - 1)}^{N-1} \left(1 - \frac{|\tau|}{N} \right)s(\tau ; \boldsymbol{\theta}) \exp ( - i \omega \tau \Delta).
\end{equation} 
This form of the expected periodogram can be shown to be equivalent to convolving the theoretical spectrum with the Fej\'{e}r kernel 
\begin{equation}
\mathcal{F}(\cdot) = \frac{\Delta}{2\pi N} \frac{\sin^{2}(N \omega \Delta/2)}{\sin^{2}(\omega \Delta /2)} 
\end{equation} \citep{Sykulski2013}. 
This approach improves the estimators obtained through maximizing the likelihood, by bypassing the problems, namely aliasing and leakage,  associated with comparison against the true spectrum. 
This leads to the final likelihood
\begin{align}
l_{b}(\boldsymbol{\theta}) = - \sum_{\omega \in \Omega} \left[\frac{\hat{S}_{z}(\omega)}{\overline{S}(\omega; \boldsymbol{\theta})} + \log \{ \overline{S} (\omega; \boldsymbol{\theta}) \}\right],
\end{align}
where $b$ denotes that this is the blurred Whittle likelihood. This likelihood is maximized by standard off-the-shelf nonlinear optimization techniques. (Specifically, \citet{Sykulski2016} uses the `fminsearchbnd' function in Matlab \citep{DErrico2006} and we use the `fminsearch' function in the `pracma' R package \citep{Borchers2015}.)

@@

\subsubsection{Significance tests for simpler models}
\label{sec: sig}
Finally, \citet{Sykulski2016} propose that a simple likelihood ratio test can be used at each time period to test whether or not a shift in the inertial oscillation has occurred. 
To do so, the authors suggest fitting a simpler five parameter model where the the parameter $\omega_{0}$ is fixed to be the inertial frequency $f_{0}$. 
Then this simpler model can be compared to the full six parameter model via a likelihood ratio test with test statistic
\begin{equation}
\label{eq: LRT}
R(t) = 2[l_{b} \{\hat{\theta}_{1}(t) \} - l_{b}\{\hat{\theta}_{0}(t) \} ],
\end{equation}
where $\hat{\theta}_{0}(t)$ is the fitted parameter vector for the simpler, or null model, and $\hat{\theta}_{1}(t)$ is the fitted parameter vector for the full model.
 The authors claim $R(t)$ then follows a chi-squared distribution with 1 degree of freedom. 
 However, as we will discuss further, this may be overly simplistic, because of potential identifiability issues with the parameters and lack of independence between time points stemming from the use of a rolling window.

@@

\begin{figure}[h!]
  \centering
    \includegraphics[width=\textwidth]{ReplicatedFigures/fig5.png}
        \caption{Left: The spectral density of one particle (blue) with the model fit overlaid for the portion of the spectra used to fit it (green) and extended to all frequencies (red). Right: The ensemble mean periodogram (blue) with the ensemble fit for the frequencies used to fit it (green) and extended to the entire spectrum (red). Individual trajectories' periodograms (light grey) and model fits (dark fit) are also displayed. }
        \label{fig: fig5}
\end{figure}

@@

   \begin{figure}[h!]
  \centering
    \includegraphics[width=\textwidth]{ReplicatedFigures/fig7.png}
        \caption{Top: Observed spectra of the drifter over time; Bottom: Modeled spectra over time. On both figures, the semi-transparent gray line indicates the average inertial frequency within the rolling window at the current time period.  Only frequencies used in the estimation are included.  }
        	\label{fig:timeVarying}
\end{figure}

 \par
 We also display the fitted parameter values over time and their 95$\%$ confidence interval bands in Figure \ref{fig: fig8}. 
The 95$\%$ intervals are obtained using numerical calculation of the Hessian.
The parameters all change smoothly over time. 
We note that the inertial frequency differs from the Coriolis Frequency from roughly days 600 to 900. 
\citet{Sykulski2016} note that this deviation is appropriate and can be explained by a change in tidal energy over shallow periods of water. 
 \begin{figure}[h!]
  \centering
    \includegraphics[width=\textwidth]{ReplicatedFigures/fig8.png}
        \caption{Estimates of the six model parameters overtime with 95$\%$ confidence interval bands. The red line in the top figure is the inertial frequency.}
        	\label{fig: fig8}
\end{figure}

 \begin{figure}[h!]
  \centering
    \includegraphics[width=.85\textwidth]{ReplicatedFigures/fig9Extend.pdf}
        \caption{Time series of the likelihood ratio test statistic comparing the 5-parameter to 6-parameter models. The dotted red line indicates the value at which test statistics indicate a significant difference between the model. The first figure uses the window size specified in \citet{Sykulski2016} and the second figure doubles the window size.}
        	\label{fig: fig9}
\end{figure}

@@

\par We, however, are skeptical of this use of simple hypothesis testing. 
The parameters are being estimated repeatedly using a rolling window. 
This means that there is not independence between the time periods and there is repeated testing. 
Both of these issues should be accounted for in designing a hypothesis test. 
Further, the authors acknowledge elsewhere in the paper that the length of the rolling window is currently selected empirically and that further work on selecting windows would be beneficial. 
This suggests that the p-value for any time point could be easily influenced by the length of the window used in fitting it.
To explore this, in Figure \ref{fig: fig9} we replicate Figure 9  in the paper using both the window length specified in the paper and a doubled window length.
The corresponding likelihood ratio tests do not reject the null hypothesis at all the same times. 
This indicates that window size and its influence on hypothesis testing should be further investigated prior to applying this formal testing approach for the presence of a shift from the Coriolis frequency.

 \begin{figure}[h!]
  \centering
    \includegraphics[width=.6\textwidth]{ReplicatedFigures/fig10.pdf}
        \caption{Table of the average correlation between parameters. Note that there are  minor differences in the correlation values between these results and those in \citet{Sykulski2016} These differences can be attributed to slight differences in the numerical optimization used by R and Matlab in calculating the Hessian. }
        	\label{fig: fig10}
\end{figure}
